Red Oak: Something Something Algorithmic Policy

### 2015-05-08 draft.tex
..

\begin{figure}[ht]
\begin{lstlisting}
f(pkt):
  if in_range(pkt, src, 0, 10) then
     if in_range pkt dst  [(0,10)] then
        deliver
     else 
        add pkt (IpDst, IpSrc) ``conn'';
        deliver
  else if in_rel pkt (IpSrc,IpDst) ``conn'' then
         deliver
       else
         RO.drop
       end
  end                
  \end{lstlisting}

@@

\section*{Decision Trees and Algorithmic Policies}

   \subsection*{Range-based Branching}
   % Why range instead of actual value, pre-generation of rules using symbolic pre-execution

  For the stateful firewall included in figure~\ref{fig:firewallcode}, the following decision tree would be generated:

  \begin{figure}

@@

>>>>

\begin{figure}[ht]
\begin{lstlisting}
f(pkt):
  if in_range(pkt, src, 0, 10) then
     if in_range pkt dst  [(0,10)] then
        deliver
     else 
        add pkt (IpDst, IpSrc) ``conn'';
        deliver
  else if in_rel pkt (IpSrc,IpDst) ``conn'' then
         deliver
       else
         drop
       end
  end                
  \end{lstlisting}

@@

From an algorithmic policy such as the one included in Fig~\ref{fig:firewall-eg}, we generate a decision tree summarizing the function's interaction with the packet and the relevant decision. The decision tree is then used by our runtime system to install switch rules and update them when necessary. For the stateful firewall included in figure~\ref{fig:firewallcode}, the following decision tree would be generated:

  \begin{figure}[ht]

@@

  This decision tree would in turn lead to the following symbolic rules:
  \begin{lstlisting}
ipsrc in [0, 100] --> Sent to Controller
ipsrc in [101, 1000], (ipsrc,ipdst) in conn
                  --> Deliver
ipsrc in [101, 1000], (ipsrc,ipdst) not in conn
                  --> Drop
  \end{lstlisting}

  At initialization, these concrete rules would be generated from the symbolic rules by having all relations be empty:
\begin{lstlisting}
ipsrc in [0, 100] ---> Sent to Controller  
ipsrc in [101, 1000] ---> Drop  
\end{lstlisting}

  When a packet is received, it is forwarded according to the first matching concrete rule installed on the switch. If the packet is sent to the controller, we evaluate the decision tree for that packet, potentially adding and removing tuples from relations, before forwarding the packet according to forwarding decision held in the relevant leaf of the decision tree. We then regenerate the concrete rules using the updated relation. For example, after having seen packet with \lstinline|ipsrc| 10 and \lstinline|ipdst| 150, the first rules would be matched, evaluating the decision tree would add tuple $(10,150)$ to relation \lstinline|conn|, the packet would be forwarded according to the forwarding decision \lstinline|Deliver|, and the concrete rules would updated as follow:

\begin{lstlisting}
ipsrc in [0, 100] ---> Sent to Controller  
ipdst = 10, ipsrc = 150 ---> Deliver  
ipsrc in [101, 1000] ---> Drop  
\end{lstlisting}

\section*{Algorithmic Policies and Decision Trees}
In this section, we describe how an algorithmic policy may interact with a packet and with relations to generate a forwarding decision, and how we build a decision tree out of an algorithmic policy.

   \subsection*{Range-based Branching}

   % Why range instead of actual value, pre-generation of rules using symbolic pre-execution
